\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Balanced margins to fit exactly one full, rich page
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.3in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Standard section headers spacing
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\titlerule\vspace{-4pt}]

% --------- COMMANDS ----------
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep, topsep=1pt, partopsep=0pt, parsep=0pt, leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, noitemsep, topsep=0pt, partopsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% -------- DOCUMENT START --------
\begin{document}

% HEADING
\begin{center}
{\Huge \textbf{SHAKTI KUMAR SAH}}\\
\vspace{4pt}
\small
\faPhone* \, +91 7643938056 \quad|\quad 
\faEnvelope \, \href{mailto:shaktisah871@gmail.com}{shaktisah871@gmail.com} \quad|\quad 
\faLinkedin \, \href{https://linkedin.com/in/shakti-kumar-sah}{linkedin.com/in/shakti-kumar-sah} \quad|\quad 
\faGithub \, \href{https://github.com/shaktisah}{github.com/shaktisah}
\end{center}

\vspace{-10pt}

% EDUCATION
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{KIIT Deemed to be University}{Bhubaneswar, India}
{B.Tech in Computer Science and Engineering (7th Semester) \textnormal{\textbar{} CGPA: 8.48 / 10}}{2023 -- 2027}

\resumeSubheading
{Alpine Secondary School}{Birgunj, Nepal}
{Intermediate in Science \textnormal{\textbar{} GPA: 3.20 / 4.0}}{2021 -- 2023}

\resumeSubheading
{Shree Maisthan Vidyapeeth Madhyamik Vidyalaya}{Birgunj, Nepal}
{Matriculation \textnormal{\textbar{} GPA: 3.85 / 4.0}}{2021}

\resumeSubHeadingListEnd

% PROJECTS
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{CodeZen | Full-Stack Online Judge \& AI Tutor}{React, Node.js, Express, MongoDB, Redis, Gemini API}
{Live: \href{https://code-zen-five.vercel.app/}{https://code-zen-five.vercel.app/}}{}
\resumeItemListStart
\resumeItem{Architected a LeetCode-style code-execution engine supporting JS, Python, C++, and Java execution via compiler sandboxes.}
\resumeItem{Integrated Gemini API with custom prompts to serve as an interactive tutor, guiding users via hints rather than solutions.}
\resumeItem{Implemented JWT authentication secured by Redis token blacklisting on user logout with TTL expiration limits.}
\resumeItem{Designed an admin dashboard for challenge CRUD operations, test cases, and user submission logs.}
\resumeItemListEnd

\resumeSubheading
{LeetCode AI Helper (Chrome Extension)}{React, Groq API, JavaScript, Chrome API}
{GitHub: \href{https://github.com/shaktisah}{github.com/shaktisah}}{}
\resumeItemListStart
\resumeItem{Developed a React Chrome extension injecting AI-powered debugging tips directly into LeetCode panels.}
\resumeItem{Integrated Groq API (Llama 3) to process code and generate contextual explanations in under 200ms.}
\resumeItem{Utilized Chrome Storage API to securely persist user configuration preferences and custom API key tokens locally.}
\resumeItemListEnd

\resumeSubheading
{Bus Booking Web App (RedBus Clone)}{React, JavaScript, HTML, CSS, Tailwind CSS}
{Live: \href{https://redbus-web.vercel.app/}{https://redbus-web.vercel.app/}}{}
\resumeItemListStart
\resumeItem{Built a responsive bus booking UI with interactive seat selection, multi-criteria filtering, and route search.}
\resumeItem{Engineered reusable React components and managed global state using React Context API.}
\resumeItem{Simulated seamless checkout flows and dynamic seat allocation using local mock databases to speed up response times.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% SKILLS
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, noitemsep, topsep=1pt, partopsep=0pt]
\item \textbf{Languages:} C++, JavaScript, Python, SQL, C
\item \textbf{Frontend:} React.js, Next.js, HTML5, CSS3, Tailwind CSS, Bootstrap
\item \textbf{Backend:} Node.js, Express.js, RESTful APIs
\item \textbf{Databases:} MongoDB (Mongoose ODM), MySQL, Redis (Caching)
\item \textbf{Tools:} Git, GitHub, VS Code, Postman, Vercel
\item \textbf{Core Academics:} Data Structures \& Algorithms (DSA), Object-Oriented Programming (OOP), DBMS, Computer Networks
\end{itemize}

% ACHIEVEMENTS
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, noitemsep, topsep=1pt, partopsep=0pt]
\item Solved \textbf{300+} Data Structures and Algorithms (DSA) problems across LeetCode and GeeksforGeeks.
\item Participated in the KIIT KONVERGE Hackathon, collaborating in a team of 4 to design a real-time web portal.
\item Conducted academic research on DDoS attack detection using Machine Learning models (Random Forest) for anomaly classification.
\item Finished in top brackets of internal programming assessments.
\end{itemize}

% CERTIFICATIONS
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, noitemsep, topsep=1pt, partopsep=0pt]
\item Database Management System (DBMS) Certification -- NPTEL (IIT Kharagpur)
\item KIIT Hackathon Participation Certificate
\end{itemize}

\end{document}
